Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-07 edubots_surveys.Rnw
typo

Initially, a single survey was developed for this purpose. Responses from 300 teachers were collected and analysed. An initial analysis of these responses led to the creation of a second survey, which collected responses from 200 different higher education teachers. The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:

\begin{itemize}
\item RQ1 - Are teachers already using messaging apps in their classes? 
\item RQ2 - Which kind of chatbots would teachers find useful in their classes? 
\item RQ3 - Which kind of interaction do teachers prefer with their students?
\item RQ4 - What kind of interaction media features do teachers value the most?
\end{itemize}

@@

%Why messaging apps are relevant here --> connect to the development of chatbots
Group messaging apps have become a powerful tool for keeping touch with students. Also, they are the baseline platform for the development of chatbots to help with the learning process. After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications. In a technology adoption model, perceived ease of use and perceived usefulness are essential. But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.

>>>>

Initially, a single survey was developed for this purpose and responses from 300 higher education teachers were collected and analysed. 
The responses' analysis entailed the creation of a second survey to which 200 teachers' responses were collected. The questions of the second 
survey focussed on discussing teachers' needs, opinions and preferences of the development of future technology-enhanced tools 
and its potential impact on educational institutions’ policies. Therefore, this paper investigated the following research questions:

\begin{itemize}
\item RQ1 - Are teachers already using messaging apps in their classes? 
\item RQ2 - Which chatbots' features would teachers find useful in their classes? 
\item RQ3 - Which kind of interaction do teachers prefer with their students?
\item RQ4 - What kind of interaction media features do teachers value the most?
\end{itemize}

@@

%Why messaging apps are relevant here --> connect to the development of chatbots
Group messaging apps have become a powerful tool for keeping touch with students. Also, many of them have built-in chatbots 
to enhance the learning process. After an initial analysis to the answers to the first survey, 
we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally 
piggybacks on another, messaging applications. In a technology adoption model, perceived ease of use and perceived usefulness are essential. But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.
